Composition-climate paper

### 2015-02-02 Composition_Ecology.Rmd
Modified `load_climate` to reflect the new model with samples in both time periods for all climate variables.
`resampling_climate` now includes `land.use` information.

Introductory text has been updated.

Climate change is rough as shit yo.

```{r fig.width=7, fig.height=6}

@@

To generate the climate niches we

#  Tree size?  Segregate

>>>>

Over the past 200 years centennial scale climate variability and land use change have interacted to transform the forests of the northeastern United States. There are clear indications that modern forests, as represented by the Forest and Inventory Analysis show greater homogeneity and significantly different species associations than pre-settlement forests [@goring2015preset]. This shift has occured over a period during which climate has begun to show the effects of anthropogenic warming, and a period in which we have increasingly used the relationship between modern tree species distributions and climate to understand future responses of tree species and forest assemblages to climate change.

If modern species distributions have been affected by land use change in a random fashion then we should expect little effect on the resulting predictions.  In the midwestern United States we see a strong gradient of temperature and precipitation that results in two major ecotones, one from prairie and savanna to closed forest, in an approixmately west to east direction, and from conifer dominated, sub-boreal forests to decidious forest in a north to south direction.  Goring et al [@goring2015preset] have shown that land use change has significantly changed the strength and structure of this ecotone, but did not examine how these shifts might affect the relationships between climate and distribution for individual taxa.

We use gridded climate data products and estimates of pre-settlement vegetation to develop climate-vegetation relationships for X major tree taxa in the upper Midwestern United States to understand how climate and land use change have interacted since Euro-American settlement to affect species distributions in the region, and to examine the possible implications of these shifts to future estimates of species resillience to climate change across the region.

@@

The analysis follows a blocked sampling method.  We generate probability density functions for actual PLSS presence, by taxon, at the settlement era and for the same PLSS space in the modern era.  We also generate climate data for the FIA presence, and we generate climate space for modern land use.  In this way we can test how much of the change in shape is the result of changing land use vs changing climate since the early part of the century.

We also develop estimates of the modern climate space that taxa would occupy if they remained in place, with only climate changing, and vice versa (need better explanation here).

Results
---------------

Discussion
----------------

Figures
--------------

References
---------------
